---
title: "Untitled"
author: "Brian Kim"
date: "10/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# ALZHEIMER'S RISK
```{r}
# Clear the Environment tab
rm(list=ls())

# Complete the 6 expressions below to identify known probabilities and their complements
pr.1st = 0.049
pr.not1st = 1 - pr.1st
pr.2nd = 0.023
pr.not2nd = 1 - pr.2nd
pr.3rd = 0.078
pr.not3rd = 1 - pr.3rd

# Run the command below AFTER completing the 6 expressions above.
cat("P(1st) = ", pr.1st, "\n",
    "P(not 1st) = ", pr.not1st, "\n","\n",
    "P(2nd) = ", pr.2nd, "\n",
    "P(not 2nd) = ", pr.not2nd, "\n","\n",
    "P(3rd) = ", pr.3rd, "\n",
    "P(not 3rd) = ", pr.not3rd, "\n","\n",
    sep="")
```

## Q1 - No additional code needed
After completing and running the setup chunk, the value for pr.2nd should be listed in your Environment tab.

## Q2 - No Code needed

## Q3. Probability all 3 have AD?
```{r}
# find prob.all3
prob.all3 = 0.049 * 0.023 * 0.078

cat("P(all3) =", prob.all3)
```

## Q4. Probability at least 1 of the 2 women has AD?
```{r}
# Hint: Find pr.none and use complementary probabilities to find pr.atleast1
pr.nofad = pr.not2nd * pr.not3rd
pr.atleast1 = 1 - pr.nofad

cat("P(>= 1 female with AD)=", pr.atleast1)
```

## Q5. No code needed

# Flu Epidemic Setup
```{r}
# Clear environment
rm(list = ls())

# Known and complementary probabilities
pr.mom = .10
pr.notmom = 1 - pr.mom
pr.dad = .20
pr.notdad =  1 - pr.dad
pr.both = .04
pr.notmom_or_notdad = (pr.notmom + pr.notdad) - (pr.notmom * pr.notdad)

# Print known and complementary probabilities
cat("P(mom) = ", pr.mom, "\n",
    "P(not mom) = ", pr.notmom, "\n","\n",
    "P(dad) = ", pr.dad, "\n",
    "P(not dad) = ", pr.notdad, "\n","\n",
    "P(both parents) = ", pr.both, "\n",
    sep = "")
```


## Q6. Probability of mom having flu given dad has flu?
```{r}
pr.mom_given_dad = (pr.mom*pr.dad)/pr.mom
cat("P(mom given dad)=", pr.mom_given_dad)
```

## Q7 & Q8 - No code needed

## Q9
```{r}
or = pr.mom + pr.dad - pr.both
or
```


## Q10 & Q11. No code needed

# PSA Test Setup
```{r}
# Clear environment
rm(list = ls())

# Participant Characteristics
n = 2950
cancer = 449
healthy = 2950 - 449

# Original test results
pos_4.0 = 0
neg_4.0 = 2950
tpos_4.0 = 0
fpos_4.0 = 0
fneg_4.0 = 449
tneg_4.0 = 2501

# Test Metrics
sensitivity_4.0 = tpos_4.0 / cancer
specitivity_4.0 = tneg_4.0 / healthy
ppv_4.0 = tpos_4.0 / pos_4.0
npv_4.0 = tneg_4.0 / neg_4.0
```


## Q12. What is the initial NPV?
```{r}
cat("NPV =", npv_4.0)
```

## Q13. No code needed.

## Q14. Percentage with an initial false negative diagnosis?
```{r}
q14percent = (fneg_4.0 / neg_4.0) * 100
cat("Percent of negatives that are false negatives = ", 
    q14percent, "%", sep="")
```

## Q15. Using a 0.6 cutoff, what percentage of true positives do we expect among those with cancer, and false positives among healthy men?
```{r}
sensitivity_0.6 = 0.93
percent_tpos_0.6 = 0.93 * 100
specificity_0.6 = 0.02
percent_fpos_0.6 = (1 - 0.02) * 100
 

cat("True positive rate = ", 
    percent_tpos_0.6, "%", 
    sep="", "\n")
cat("False positive rate = ", 
    percent_fpos_0.6, "%", 
    sep="")
```

## Q16. How many false negatives with a 1.1 cutoff?
```{r}
tpos1.1 = 449 * 0.75
fneg_1.1 = 449 - tpos1.1

cat("false negatives =", fneg_1.1)
```

# Q17. How many false positives with a 1.1 cutoff?
```{r}
tneg1.1 = 0.33 * 2501
fpos_1.1 = 2501 - tneg1.1

cat("false positives =", fpos_1.1)
```

## Q18
```{r}
ppv_1.1 = (449 * 0.75)/(fpos_1.1+tpos1.1)
npv_1.1 = (2501 * 0.33)/(tneg1.1 + fneg_1.1)



cat("PPV for a 1.1 cutoff =", ppv_1.1, "\n")
cat("NPV for a 1.1 cutoff =", npv_1.1)
```

## Q19 - You may use the below to work through the answer options. You may find some of the information already exist in your Environment tab.
```{r}

```

## Q20 - no code needed
