---
title: "Lab13"
author: "Marissa Ehringer"
date: "11/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Call libraries needed
```{r}
library(tidyverse)
library(ggplot2)
```

# Question 1 - no code needed

# Question 2 - create one-way table and run Chi-square
```{r}
# Create a one-way table
flower <- matrix(c(54,122,58), ncol =3, byrow=TRUE)
flower <- as.table(flower)
flower
# Add column and row names
colnames(flower) <- c("red","pink","white")
rownames(flower) <- c("counts")
flower
# run the Chi-square test by listing the expected frequencies
chisq.test(flower, p=c(.25,  .50,  .25))
```
# Question 3 - create a two-way table and run Chi-Square
```{r}
# create a two-way table
angina <- matrix(c(44, 19, 116, 128),ncol=2,byrow=TRUE)
angina <- as.table(angina)
angina
# add column and row names
colnames(angina) <- c("Timolol","Placebo")
rownames(angina) <- c("No Attacks", "Angina Attacks")
# run the Chi-square test
chisq.test(angina)

```

# Import data and recode factor variables
```{r}
nicgenes <- read.csv("Lab13_nicgenes.csv")
nicgenes$SEX <- factor(nicgenes$SEX)
nicgenes$SEX <- fct_recode(nicgenes$SEX, "female"= "0", "male" = "1")
nicgenes$TOBEVER <- factor(nicgenes$TOBEVER)
nicgenes$TOBEVER <- fct_recode(nicgenes$TOBEVER, "yes"="1", "no"="0")
nicgenes$ALCEVER <- factor(nicgenes$ALCEVER)
nicgenes$ALCEVER <- fct_recode(nicgenes$ALCEVER, "yes"="1", "no"="0")
nicgenes$TOB4 <- factor(nicgenes$TOB4)
nicgenes$TOB4 <- fct_recode(nicgenes$TOB4, "NoTobDep"="1", "TobDep"="3", "TobDepSym"="4")
nicgenes$ALC4 <- factor(nicgenes$ALC4)
nicgenes$ALC4 <- fct_recode(nicgenes$ALC4, "NoAlcDep"="1", "AlcAb"="2", "AlcDep"="3", "AlcDepSym"="4")
nicgenes$subjecttype <- factor(nicgenes$subjecttype)
nicgenes$subjecttype <- fct_recode(nicgenes$subjecttype, "clinical"="1", "control"="0")

```

# Question 4 - how many clinical subjects
```{r}
# insert code here
summary(nicgenes)
```

# Question 5 - how many male subjects
```{r}
# insert code here
```

# Question 6 - plot TOBEVER variable by sex
```{r}
ggplot(nicgenes) +
  aes(x = TOBEVER) +
  geom_bar() +
  labs(x="Ever used tobacco",
       y="Number of subjects") +
  facet_wrap(nicgenes$SEX)
```


# Question 7 - Create a table for sex and tobever
```{r}
# insert code here

```

# Question 8 - Use table data to do Chi-square
```{r}
# make table
tbl <-table(nicgenes$TOBEVER, nicgenes$SEX)
tbl
chisq.test(tbl)


# add column and row names


# run the Chi-square test

```
# Question 9 - perform Chi-square on raw data
```{r}
chisq.test(nicgenes$SEX, nicgenes$TOBEVER)
```
# Question 10 - Test for association between TOBEVER and ALCEVER
```{r}
# insert code here
tbl2 <-table(nicgenes$TOBEVER, nicgenes$ALCEVER)
tbl2
chisq.test(tbl2)
```

# Question 11 - TOB4 and ALC4
```{r}
# insert code here

```



# Question 12 - Combine TOB4 and ALC4 levels 3 and 4
```{r}
nicgenes$TOB4c <- nicgenes$TOB4 %>%
  fct_recode("NoTobDep" = "NoTobDep",
             "TobDep" = "TobDep",
             "TobDepS" = "TobDepSym")
nicgenes$ALC4c <- nicgenes$ALC4 %>%
  fct_recode("NoAlcDep" = "NoAlcDep",
             "AlcAb" = "AlcAb",
             "AlcDep" = "AlcDep",
             "AlcDepS" = "AlcDepSym")
# check that you did it correctly
table(nicgenes$TOB4c,nicgenes$ALC4c)
# rerun Chi-square


```

# Question 13 - test for association between tobacco ever and all SNPs
```{r}
chisq.test(nicgenes$TOBEVER, nicgenes$rs4950)
chisq.test(nicgenes$TOBEVER, nicgenes$rs684513)
chisq.test(nicgenes$TOBEVER, nicgenes$rs680244)
chisq.test(nicgenes$TOBEVER, nicgenes$rs514743)
chisq.test(nicgenes$TOBEVER, nicgenes$rs8040868)
chisq.test(nicgenes$TOBEVER, nicgenes$rs11637630)
chisq.test(nicgenes$TOBEVER, nicgenes$rs1948)
```

# Question 14 - Test for association between SNPs and TOB4
```{r}
chisq.test(nicgenes$TOB4, nicgenes$rs4950)
chisq.test(nicgenes$TOB4, nicgenes$rs684513)
chisq.test(nicgenes$TOB4, nicgenes$rs680244)
chisq.test(nicgenes$TOB4, nicgenes$rs514743)
chisq.test(nicgenes$TOB4, nicgenes$rs8040868)
chisq.test(nicgenes$TOB4, nicgenes$rs11637630)
chisq.test(nicgenes$TOB4, nicgenes$rs1948)
```
# Question 15 - no code needed

# Question 16 - no code needed
```{r}
dbinom(1,7,0.5)
```
# Question 17 - no code needed

# Question 18 - no code needed

# Question 19
```{r}
test1 <- chisq.test(nicgenes$TOBEVER, nicgenes$rs4950)$p.value
test2 <- chisq.test(nicgenes$TOBEVER, nicgenes$rs684513)$p.value
test3 <- chisq.test(nicgenes$TOBEVER, nicgenes$rs680244)$p.value
test4 <- chisq.test(nicgenes$TOBEVER, nicgenes$rs514743)$p.value
test5 <- chisq.test(nicgenes$TOBEVER, nicgenes$rs8040868)$p.value
test6 <- chisq.test(nicgenes$TOBEVER, nicgenes$rs11637630)$p.value
test7 <- chisq.test(nicgenes$TOBEVER, nicgenes$rs1948)$p.value

tests <- c(test1, test2, test3, test4, test5, test6, test7)

p.adjust(p=tests, method = "hochberg")
```






